Enhancement of SDR in Thessaloniki

### 2024-01-21 GHI_enh_04_investigate.tex
Commit 2024-01-21 16:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-18}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

Tourpali: 1.7152 0.1817 9.4404 0

@@

Tourpali: 1.1004 0.255 4.3146 0

@@

Tourpali: -0.1679 3.8757 -0.0433 0.9654

@@

Tourpali: 605.7835 145.2351 4.1711 0

@@

Tourpali: 0.003 4e-04 7.7371 0

@@

Tourpali: 0.0018 5e-04 3.3956 7e-04

@@

Tourpali: 1.0386 0.2143 4.8455 0

@@

Tourpali: 0.7132 0.1476 4.8325 0

@@

Tourpali: 0.1206 0.0487 2.4752 0.0133

@@

Tourpali: 0.5126 0.0703 7.2901 0

@@

Tourpali: 28.0362 4.3653 6.4225 0

@@

Tourpali: 0.0011 2e-04 6.6404 0

@@

Tourpali: 3e-04 1e-04 3.7461 2e-04

@@

Tourpali: 0.0356 0.0048 7.3697 0

@@

Tourpali: -0.1021 0.5303 -0.1925 0.8473

@@

Tourpali: -0.249 0.4778 -0.5212 0.6022

@@

Tourpali: 0.024 0.0229 1.0454 0.2959

@@

Tourpali: 4.6804 5.0982 0.9181 0.3586

@@

Tourpali: 3e-04 3e-04 1.0722 0.2836

@@

Tourpali: 1e-04 2e-04 0.8844 0.3765

@@

Tourpali: 0.007 0.0063 1.1208 0.2624

@@

@@

\begin{verbatim}
2024-01-18 15:45:20.0 athan@sagan GHI_enh_04_investigate.R 0.179315 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-21}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

Attaching package: 'zoo'
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:base':

    as.Date, as.Date.numeric
\end{verbatim}

\begin{verbatim}
ST_daily ST_E_daily ST_E_daily_seas ST_extreme_daily
\end{verbatim}

@@

Arima: 1.7152 0.1817 9.4404 0

@@

Arima: 1.1004 0.255 4.3146 0

@@

Arima: -0.1679 3.8751 -0.0433 0.9654

@@

Arima: 605.7835 145.2351 4.1711 0

@@

Arima: 0.003 4e-04 7.7371 0

@@

Arima: 0.0018 5e-04 3.3956 7e-04

@@

Arima: 1.0386 0.2143 4.8455 0

@@

Arima: 0.7132 0.1476 4.8325 0

@@

Arima: 0.1206 0.0487 2.4752 0.0133

@@

Arima: 0.5126 0.0703 7.2901 0

@@

Arima: 28.0362 4.3654 6.4224 0

@@

Arima: 0.0011 2e-04 6.6404 0

@@

Arima: 3e-04 1e-04 3.7461 2e-04

@@

Arima: 0.0356 0.0048 7.3697 0

@@

Arima: -0.1021 0.5303 -0.1925 0.8473

@@

Arima: -0.249 0.4778 -0.5212 0.6022

@@

Arima: 0.024 0.0229 1.0454 0.2959

@@

Arima: 4.6804 5.0982 0.9181 0.3586

@@

Arima: 3e-04 3e-04 1.0722 0.2836

@@

Arima: 1e-04 2e-04 0.8844 0.3765

@@

Arima: 0.007 0.0063 1.1208 0.2624

@@

\hypertarget{group-stats}{%
\subsubsection{Group stats}\label{group-stats}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-3} \end{center}

\hypertarget{energy-contribution-of-enhancements}{%
\subsubsection{Energy contribution of enhancements}\label{energy-contribution-of-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-4} \end{center}

\hypertarget{sza-enhancements}{%
\subsubsection{SZA enhancements}\label{sza-enhancements}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-3} \end{center}

@@

\begin{verbatim}
2024-01-21 11:10:50.8 athan@tyler GHI_enh_04_investigate.R 1.035152 mins
\end{verbatim}
